As a part of a team of 6, I conducted 2 key projects that brought 60\% of the company’s revenue.

\begin{itemize}
    \item Led one of the key projects that support 100+ active companies: planned sprints and releases, resolving critical user issues together with the Support team.
    \item Built a \href{https://www.ajot.com/news/karta.io-introduces-a-new-sub-accounts-feature-delivering-an-advanced-money-flow-operation}{\underline{Sub Accounting System}} from scratch for 1000 active clients to give them the availability to split one account into several buckets and managed them independently which led to the opening of 17k+ subaccounts.
    \item Increased the number of providers from 1 to 3 by redesigning the architecture of the core part of the system. Speeded up new providers implementation from 3 months to 2 weeks and increased the number of opened cards for key clients by 0,7\%.
    \item Saved 42 working hours monthly by building an analytics tool kit that allows the business to quickly implement events and test product hypotheses.
    \item Built a \href{https://karta.io/blog/21-meet-karta-api-growth-engine-for-your-business}{\underline{public API}} so clients can integrate opening financial accounts, issuing cards, and processing card transactions.
    \item Founded a Book Club for a team of 5 to read professional IT books weekly and see how to implement this in our job.
    \item Built relationships with 20+ team members: Developers, Analytics, QAs, Product Managers, Support, and Designers.
    \item During 3 months mentored 1 Junior Python Developer which led to passing the probation period.
\end{itemize}

